Supplementary Figures relative to feature selection

### 2020-06-29 supplementary_figures/supp_overall.Rmd
simplified labels, reduced text size

```{r, fig.width=7, fig.height=6}
ov <- readRDS("../data/overall.rds")

@@

ff <- function(x, trueK=FALSE){
  f <- paste0(x,"~dataset+resolution*dataset+doubletmethod+filt+norm+clustmethod+dims")
  if(trueK) cl <- cl[cl$n_clus==cl$true.nbClusts,]
  mod <- lm(as.formula(f), data=cl)
  co <- as.data.frame(coef(summary(mod)))
  co <- co[grep("sctransfrom|scran|filt|elbow|doublet|Annoy", row.names(co)),]
  colnames(co)[2:4] <- c("stderr","t","pvalue")
  co$coef <- gsub(" +$","",row.names(co))
  aov <- as.data.frame(summary(aov(mod))[[1]])[,-1]
  aov <- aov[grep("^Residuals|resolution|dataset", row.names(aov), invert=TRUE),]
  aov$varExpl <- aov[,1]/sum(aov[,1])
  aov <- aov[grep("^Residuals", row.names(aov), invert=TRUE),4:5]
  colnames(aov)[1] <- "pvalue"
  aov$parameter <- gsub(" +$","",row.names(aov))
  list( coefs=co, aov=aov )
}

@@

co <- dplyr::bind_rows(lapply(cos, FUN=function(x) x$coef), .id="metric")
co2 <- dplyr::bind_rows(lapply(cos2, FUN=function(x) x$coef), .id="metric")
for(f in c("norm","filt","doubletmethod","dims","clustmethod")){
  co$coef <- gsub(paste0("^",f),"",co$coef)
  co2$coef <- gsub(paste0("^",f),"",co2$coef)
}
p3 <- ggplot(co, aes(coef, Estimate, group=coef, fill=metric)) + geom_col() + xlab("") +
  ylab("Estimated coefficient") + geom_hline(yintercept = 0, linetype="dashed") + 
  coord_flip() + theme(legend.position="none")
p4 <- ggplot(co2, aes(coef, Estimate, group=coef, fill=metric)) + geom_col() + xlab("") +
  ylab("Estimated coefficient") + geom_hline(yintercept = 0, linetype="dashed") + 
  coord_flip() + theme(legend.position="none")

@@

`metric ~ dataset*resolution+doubletmethod+filt+norm+clustmethod+dims`

@@

```{r}
rnfn <- function(x){
  x <- gsub("^norm\\.","",x)
  x <- gsub("^doublet\\.","",x)
  x <- gsub("> none > ","> no filter > ",x)
  gsub("^none > ","",x)
}

H1 <- renameHrows( scrna_evalPlot_silh(ov, agg.by = c("doubletmethod","filt","norm"), row_split = norm,
                                       heatmap_legend_param=list(direction="horizontal"),font_factor = 0.8,
                                       row_names_max_width=unit(7, "cm")), rnfn)
H2 <- renameHrows(
     evalHeatmap(ov, step="clustering", what=c("MI","min_pr"), anno_legend=FALSE, title=c("MI","Min precision"), 
                 agg.by=c("doubletmethod","filt","norm"), font_factor = 0.8, 
                 row_split=norm,row_names_max_width=unit(7, "cm")) + 
    evalHeatmap(ov, step="clustering", what=c("ARI"), agg.by=c("doubletmethod","filt","norm"), 
                row_split=norm,filter=n_clus==true.nbClusts, title="ARI at true k",
                anno_legend=FALSE, font_factor = 0.8,row_names_max_width=unit(7, "cm")),
  rnfn)

H3 <- renameHrows( scrna_evalPlot_silh(ov, agg.by = c("doubletmethod","sel","norm"), row_split = norm,
                                       heatmap_legend_param=list(direction="horizontal"),
                                       row_names_max_width=unit(7, "cm")), rnfn)
H4 <- renameHrows(
     evalHeatmap(ov, step="clustering", what=c("MI","min_pr"), anno_legend=FALSE, title=c("MI","Min precision"),
                 agg.by=c("doubletmethod","sel","norm"), row_split=norm,row_names_max_width=unit(7, "cm")) + 
    evalHeatmap(ov, step="clustering", what=c("ARI"), agg.by=c("doubletmethod","sel","norm"), 
                row_split=norm,filter=n_clus==true.nbClusts, title="ARI at true k", 
                anno_legend=FALSE, row_names_max_width=unit(7, "cm")),
  rnfn)
```

>>>>

```{r, fig.width=6, fig.height=5}
ov <- readRDS("../data/overall.rds")

@@

ff <- function(x, trueK=FALSE){
  f <- paste0(x,"~dataset+resolution*dataset+doubletmethod+sel+filt+norm+clustmethod+dims")
  if(trueK) cl <- cl[cl$n_clus==cl$true.nbClusts,]
  mod <- lm(as.formula(f), data=cl)
  co <- as.data.frame(coef(summary(mod)))
  co <- co[grep("sctransfrom|scran|filt|elbow|doublet|Annoy", row.names(co)),]
  colnames(co)[2:4] <- c("stderr","t","pvalue")
  co$coef <- gsub(" +$","",row.names(co))
  aov <- as.data.frame(summary(aov(mod))[[1]])[,-1]
  aov <- aov[grep("^Residuals|resolution|dataset", row.names(aov), invert=TRUE),]
  aov$varExpl <- aov[,1]/sum(aov[,1])
  aov <- aov[grep("^Residuals", row.names(aov), invert=TRUE),4:5]
  colnames(aov)[1] <- "pvalue"
  aov$parameter <- gsub(" +$","",row.names(aov))
  list( coefs=co, aov=aov )
}

@@

co <- dplyr::bind_rows(lapply(cos, FUN=function(x) x$coef), .id="metric")
co2 <- dplyr::bind_rows(lapply(cos2, FUN=function(x) x$coef), .id="metric")
for(f in c("norm","filt","doubletmethod","dims","sel","clustmethod")){
  co$coef <- gsub(paste0("^",f),"",co$coef)
  co2$coef <- gsub(paste0("^",f),"",co2$coef)
}
p3 <- ggplot(co, aes(coef, Estimate, group=coef, fill=metric)) + geom_col() + xlab("") +
  ylab("Estimated coefficient") + geom_hline(yintercept = 0, linetype="dashed") + 
  coord_flip() + theme(legend.position="none")
p4 <- ggplot(co2, aes(coef, Estimate, group=coef, fill=metric)) + geom_col() + xlab("") +
  ylab("Estimated coefficient") + geom_hline(yintercept = 0, linetype="dashed") + 
  coord_flip() + theme(legend.position="none")

@@

`metric ~ dataset*resolution+doubletmethod+filt+sel+norm+clustmethod+dims`

@@

```{r}
rnfn <- function(x){
  x <- gsub("norm\\.","",x)
  x <- gsub("^doublet\\.","",x)
  x <- gsub("> none > ","> no filter > ",x)
  gsub("^none > ","",x)
}

H1 <- renameHrows( scrna_evalPlot_silh(ov, agg.by = c("doubletmethod","filt","norm"), row_split = rnfn(norm),
                                       heatmap_legend_param=list(direction="horizontal"),font_factor = 0.8,
                                       row_names_max_width=unit(7, "cm")), rnfn)
H2 <- renameHrows(
     evalHeatmap(ov, step="clustering", what=c("MI","min_pr"), anno_legend=FALSE, title=c("MI","Min precision"), 
                 agg.by=c("doubletmethod","filt","norm"), font_factor = 0.8, 
                 row_split=rnfn(norm),row_names_max_width=unit(7, "cm")) + 
    evalHeatmap(ov, step="clustering", what=c("ARI"), agg.by=c("doubletmethod","filt","norm"), 
                row_split=rnfn(norm),filter=n_clus==true.nbClusts, title="ARI at true k",
                anno_legend=FALSE, font_factor = 0.8, row_names_max_width=unit(7, "cm")),
  rnfn)

H3 <- renameHrows( scrna_evalPlot_silh(ov, agg.by = c("doubletmethod","sel","norm"), row_split = rnfn(norm),
                                       heatmap_legend_param=list(direction="horizontal"),
                                       font_factor = 0.8, 
                                       row_names_max_width=unit(7, "cm")), rnfn)
H4 <- renameHrows(
     evalHeatmap(ov, step="clustering", what=c("MI","min_pr"), anno_legend=FALSE, title=c("MI","Min precision"),
                 agg.by=c("doubletmethod","sel","norm"), row_split=rnfn(norm), 
                 font_factor = 0.8, row_names_max_width=unit(7, "cm")) + 
    evalHeatmap(ov, step="clustering", what=c("ARI"), agg.by=c("doubletmethod","sel","norm"), 
                row_split=rnfn(norm),filter=n_clus==true.nbClusts, title="ARI at true k", 
                anno_legend=FALSE, font_factor = 0.8, row_names_max_width=unit(7, "cm")),
  rnfn)
```
